Results

### 2018-08-22 3-simus.Rmd
save

>>>>

### Scenario n°1 (comparison with biglasso)

```{r}
library(biglasso)
library(Matrix)
```

```{r, eval=FALSE}
G3 <- bigmemory::big.matrix(nrow(G), ncol(G) + ncol(covar.all),
                            backingfile = "G-PC",                 
                            backingpath = "backingfiles")
big_apply(G, function(X, ind) { G3[, ind] <- X[, ind]; NULL }, a.combine = 'c')
G3[, ncol(G) + cols_along(covar.all)] <- covar.all
```

```{r}
G3 <- bigmemory::attach.big.matrix("backingfiles/G-PC.desc")
```

```{r}
logit.biglasso <- function(G3, pheno.all, covar.all, ind.train, ind.test) {

  timing <- system.time({

    biglasso <- biglasso(G3, pheno.all, ind.train, ncores = nb_cores(),
                         penalty = "lasso", alpha = 1, family = "binomial")

    preds <- 1 / (1 + exp(-predict(biglasso, G3, ind.test)))
  })[3]

  aucs <- apply(preds, 2, bigstatsr::AUC, target = pheno.all[ind.test])
  ind.max <- which.max(aucs)

  tibble(
    method   = "biglasso", 
    pred     = list(preds[, ind.max]),
    timing   = timing,
    alpha    = 1,
    set      = list(which(head(biglasso$beta[, ind.max], -ncol(covar.all)) != 0))
  )
}
```

```{r}
params.grid7 <- expand.grid(
  n.train = 6000,
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.8), 
  par.model  = c("simple"),
  num.simu   = 1:100,
  stringsAsFactors = FALSE
) 
```

```{r, eval=TRUE}
if (!dir.exists("results7")) dir.create("results7")

for (i in rows_along(params.grid7)) {

  res.file <- paste0("results7/simu_", i, ".rds")
  if (file.exists(res.file)) next

  params <- params.grid7[i, ]
  par.causal <- params[["par.causal"]][[1]]

  # Get results from all methods
  res <- bind_rows(
    logit.CMSA(G, pheno.all, covar.all, ind.train, ind.test, "logit-simple", alphas = 1),
    logit.biglasso(G3, pheno.all, covar.all, ind.train, ind.test)
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### 2018-08-22 4-results-simus.Rmd
save

```{r, message=FALSE}
COLORS <- scales::hue_pal()(6)
methods.color <- setNames(
  c(COLORS, COLORS[c(4, 2, 5)]), 
  c("logit-simple", "PRS-max", "PRS-stringent", "T-Trees", "logit-triple", "PRS-all",
    "PRS-max-0.05", "PRS-max-0.2", "PRS-max-0.8")
) 
```

@@

>>>>

```{r, message=FALSE}
COLORS <- scales::hue_pal()(6)
methods.color <- setNames(
  c(COLORS, COLORS[c(4, 2, 5)], "black"), 
  c("logit-simple", "PRS-max", "PRS-stringent", "T-Trees", "logit-triple", "PRS-all",
    "PRS-max-0.05", "PRS-max-0.2", "PRS-max-0.8", "biglasso")
) 
```

@@

### Comparison with biglasso

```{r, fig.asp=0.65, out.width="95%", fig.width=16}
list.files("results7", full.names = TRUE) %>%
  read_format_results(corr) %>%
  compare_logit("biglasso")

ggsave("figures/supp-biglasso.pdf", scale = 1/100, width = 1600, height = 1000)
```
